---
title: "methods-4-c-2"
author: "Ditlev K"
date: "2023-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse, ggplot2)

```

## Rethinking

```{r}
install.packages(c("coda","mvtnorm","devtools","loo","dagitty","shape"))
devtools::install_github("rmcelreath/rethinking")

library(rethinking)
```


``````{r 3E1}
p_grid <- seq( from=0 , to=1 , length.out=1000 )
prior <- rep( 1 , 1000 )
likelihood <- dbinom( 6 , size=9 , prob=p_grid )
posterior <- likelihood * prior
posterior <- posterior / sum(posterior)
set.seed(100)
samples <- sample( p_grid , prob=posterior , size=1e4 , replace=TRUE )

#3E1. How much posterior probability lies below p = 0.2?
#3E2. How much posterior probability lies above p = 0.8?
#3E3. How much posterior probability lies between p = 0.2 and p = 0.8?
#3E4. 20% of the posterior probability lies below which value of p?
#3E5. 20% of the posterior probability lies above which value of p?
#3E6. Which values of p contain the narrowest interval equal to 66% of the posterior probability?
#3E7. Which values of p contain 66% of the p 

plot( p_grid , posterior , type="b" ,
xlab="probability of water" , ylab="posterior probability" )
mtext( "1000 points" )

dens(samples)

sum( samples < 0.2 ) /1e4

sum( samples > 0.8 ) /1e4

sum( samples > 0.2 & samples < 0.8 ) / 1e4

quantile( samples , 0.2 )

quantile( samples, 0.8 )

HPDI( samples , prob=0.66 )
```




